---
title: "Workflow for Automated Handling of Submission Emails"
author: "Sally A.M. Hogenboom"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    self_contained: false
vignette: >
  %\VignetteIndexEntry{Receive & Process Submission Emails}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(yOUrEmail)
library(magrittr)
```

# Authentication

**Goal**

Create a successful connection to the outlook environment. 
This connection allows us to read/write/send emails from an (automated) R script.

**Requirements**

  * Login credentials for our business outlook
  * An active browser (e.g., Microsoft Edge)
  * A Windows Computer
  * `install.packages("httpuv")` 
  
**Execution**

```{r authentication}
# Authenticate & get Outlook Environment
outlook <- Microsoft365R::get_business_outlook()
```

**Expected Behavior**

Upon first login this code prompts a manual login process via the browser. Working with Windows/Microsoft Edge allows for our login credentials to be saved (automatically). Therefore, upon subsequent authentication the credentials will be updated (see message output in code above).

**Development To Do's**

1. It is highly plausible that this workflow only works with a `Windows` x `Microsoft Edge` combination. Workarounds for unattended scripts (i.e., no manual steps) are available via a [Microsoft365R vignette](https://cran.r-project.org/web/packages/Microsoft365R/vignettes/scripted.html).
1. I have not been able to implement a test for an unsuccessful authentication process (see `test-authentication.R`).

# Retrieve All Submissions

**Goal**

Retrieve all new (i.e., unread) emails from the submission system.

**Requirements**

  * [Outlook Authentication](#authentication)
  
**Execution**

* `outlook`: pass down the outlook environment retrieved during successful authentication
* `submissions_folder`: specify the folder where the submissions are received. 
Some teachers have automated rules set-up which move the submissions to a different
folder (e.g., 'Nakijken'). If this is the case, specify the exact name of that folder.
* `submissions_email`: built-in option to allow for upcoming changes to the submissions system which will send the submissions from a different emailadres.
* `email_status`: unread/read/all

```{r get-submissions}
submissions <- get_submissions(outlook,
  submissions_folder = "Nakijken",
  submissions_email = "submit@oupsy.nl",
  email_status = "unread"
)
```

**Expected Behavior**

* Retrieve a list of emails with class `ms_outlook_email`

**Development To Do's**

* *None*

# One Email Workflow
This is a workflow for one email. This allows for a better step-by-step testing
and understanding. See [automated_flow]
## Extract Information

**Goal**

Process the contents of the email to extract the relevant information:

  * `course_id` unique identifier with two letters (e.g., PB for Psychology Bachelor) and four numbers
  * `course_name` human readable name of the course
  * `course_run` courses can have different versions (i.e., runs). The course run determines which grading form should be used for the submission.
  * `student_number` unique numeric identifier for each student.
  * `student_name` name as parsed from the student's email account.
  * `student_email` email adress provided by the student which is used to communicate the attained grade with students.
  * `submission_date` date on which the email/submission was received.
  * `submission_note` students have the option to add a note for the teacher. If such a note was provided it is also extracted.
  
Added additional relevant content:
  * `grade_before_date` compute the date before which the grading should be finished (20 working days from submission).
  * `grade_status` add a default 'to do' status for use in the grading_overview (see below).

**Requirements**

  * An email from the submission system with class `ms_outlook_email`
  * `install.packages("qdapRegex")`
  
**Execution**

```{r get-submission-info}
# Example: one email
submission_info <- get_submission_info(
  email = submissions[[1]],
  n_workdays = 20
)
```

**Expected Behavior**

A tibble with `r ncol(submission_info)` columns: (`r glue::glue_collapse(colnames(submission_info), sep = ", ", last = ", en ")`). The number of rows depends on
the number of emails that were processed (i.e., `nrow(submission_info) == length(submissions)`).

**Development To Do's**

1. Additional information to add:

    * `course` the conventional name for the course (e.g., Onderzoekspracticum Experimenteel Onderzoek).
    * `course_id` the numeric identifier for the course. This can be the same as the course_run if no versions of the course exist in the submission system. 

1. Currently, when computing the `grade_before_date` a shortcut was made to
compute the date with the number of working days from the `submission_date`. 
In doing so, we do not account for national holidays such as Christmas or Koningsdag.
Without accounting for these holidays the `grade_before_date` can at times be a
couple of days earlier than necessary - but earlier grading does not affect the students negatively.

1. Write tests to account for emails with missing information. Low priority due to the fact that emails are automatically generated with a standardized structure.


## Create File Structure

**Goal**
Each submission is stored according to a standardized file structure: `course` > `course_run` > `student `. For new submissions this file structure does not yet exist and is therefore created before saving the submission attachments.

**Requirements**

  * The parsed contents of a new submission email
  * Administrative rights allowing the creation of new folders
  * This file should be nested within an R project that also (will) contain(s) the student submissions.
  
**Execution**

```{r, eval = FALSE}
# Example: one email
student_folder <-
  create_folder_structure(submission_info,
    grading_folder = here::here("Ingeleverde Opdrachten")
  )
```

**Expected Behavior**

* Create a nested file structure with the format: `grading_folder` > `course_id` > `course_run` > `student_folder`.
* Return the path to the student folder for use in subsequent code.

**Development To Do's**

*none*

## Extract and Save Attachments

**Goal**

Extract the attachments from the email and place them in the designated student
folder.

**Requirements**

  * email with class `ms_outlook_email`
  * file path to the student's folder
  
**Execution**

```{r, eval = FALSE}
# Invisible to prevent list output of 'NULL' results.
invisible(
  download_attachments(
    email = submissions[[1]],
    student_folder = student_folder
  )
)
```

**Expected Behavior**

* All attachments are downloaded and stored in the `course` > `course_run` > `student` folder.
* All attachments are renamed to the short and standardized format.

**Development To Do's**

1. Research how to prevent the list of NULL results from within the `download_attachments` function. Tried invisible `attachment$download()` but that did not change anything.


## Add Grading Form

**Goal**
* Select the correct grading form (dependent on `course` > `course_run`) and add it to the student's folder.
* Update the file name to include the student's details. Keep it in the same format as the files that were received from the submission system.

**Requirements**

Grading forms differ in their naming conventions. In addition, some courses see a different grading form for each `course_run`, while others keep the same form for years. To prepare this step, a human must once add & update the name of each grading form manually. The `grading_form_folder` must have the following structure:

* A folder for each `course` (e.g., `PB0812`)
* A grading form for each `course_run` (e.g., `PB0812202144.xlsx`)

Technically, to get started only those grading forms need to be added from courses where new submissions can be expected (1-year after course start).

**Execution**

```{r, eval = FALSE}
invisible(
  move_grading_form(
    grading_form_folder = here::here("Beoordelingsformulieren"),
    student_folder = student_folder,
    submission_info = submission_info
  )
)
```

**Expected Behavior**

The required grading form is copied from the `grading_form_folder` to the `student_folder`. The name is changed to align with the naming conventions of the other received documents.

**Development To Do's**

1. Resolve printing `FALSE` after executing the function.


## Update Submission Overview

**Goal**

Update the current submission overview with the latest submission. 
Reorder the overview such that the 'To Do's' are at the top, with the most urgent
grading (i.e., closest `grade_before_date`) at the top.

**Requirements**

  * The `submission_info`
  * The name of the `submission_overview`, which if it doesn't yet exist will 
  be created.
  
**Execution**

```{r, eval = FALSE}
update_submission_overview(
  submission_info = submission_info,
  submission_overview = here::here("NakijkOverzicht.xlsx")
)
```

**Expected Behavior**

* An excel sheet with the name of `submission_overview` is created which contains
the most recent and historic `submission_info`.

**Development To Do's**

1. Conditional formatting
1. Compute a 'grade_by_n_days` or add an excel formula
1. Complete historic information from read outlook emails.
1. Prevent warnings from showing

## Mark As Read

```{r}
# Mark email as processed
invisible(submissions[[1]]$update("isRead" = TRUE))
```


## Send Confirmation

**Goal**

Send a confirmation email to the student which contains:
1. A general confirmation that the assignment was received
1. A general statement of being able to expect the grading at the latest
before the `grade_before_date`.

**Requirements**

  * The `submission_info` from a single submission as extracted in the step above.
  * The `email` content to allow a reply to the correct email (for keeping easy inbox structures)
  * `install.packages("blastula")`
  
**Execution**

> *NOTE: upon executing this code an actual email is send!*

```{r, eval = FALSE}
# Example: one email
send_confirmation_email(
  outlook = outlook,
  submission_info = get_submission_info(email = submissions[[1]]),
  email = submissions[[1]],
  teacher_name = "Sally"
)
```

**Expected Behavior**

An actual email is send to the student's email adress to confirm receiving a new submission.

**Development To Do's**

1. Optimize the styling of the email such that it includes the OU house style, a logo, the correct font, a formal email signature, and a footer.
1. Check whether existing footers are added below the created email.

## Plagiarism Scan

**Goal**

Forward the email, containing only the relevant files, to the plagiarism scan software.

**Requirements**

 * The `email` with class `ms_outlook`
 * A personal email adres linked to Urkund
  
**Execution**

```{r, eval = FALSE}
forward_plagiarism_scan(email = submissions[[1]],
                        student_folder = student_folder,
                        urkund_email = "sally.hogenboom.ounl@analysis.urkund.com")

```

**Expected Behavior**

* An email is send to the `urkund_email` adres which includes the report (i.e., `verslag`) as attachment.

**Development To Do's**

1. Normally you would forward the email to the urkund email adress while removing the irrelevant attachments. However, this is not possible in the `Mircosoft365R` package for two reasons. First, creating a 'forward' email takes a crazy amount of time. Second, each attachments that is removed requires a manual confirmation in an alert pop-up. This prevents it from implementation as part of an automated workflow.
1. Because of this issue the current workflow does not allow for the plagiarism email to become part of the email 'thread'.


# Multi Email Workflow

**Goal**

Process all the new submissions as part of an `apply` loop.

**Requirements**

  * Authorization
  * All submissions
  
**Execution**

```{r, eval = FALSE}

lapply(
  X = submissions,
  FUN = function(email) {
    # Get information from the submission email
    submission_info <-
      get_submission_info(
        email = email,
        n_workdays = 20
      )

    # Create File Structure
    student_folder <-
      create_folder_structure(submission_info,
        grading_folder = "Ingeleverde Opdrachten"
      )

    # Download Attachments
    download_attachments(
      email,
      student_folder
    )

    # Add grading forms
    move_grading_form(student_folder,
      submission_info,
      grading_form_folder = "Beoordelingsformulieren"
    )

    # Update submission overview
    update_submission_overview(submission_info,
      submission_overview = here::here("NakijkOverzicht.xlsx")
    )

    # Mark email as processed
    invisible(email$update("isRead" = TRUE))

    # Send Confirmation email
    invisible(send_confirmation_email(outlook,
      submission_info,
      email,
      teacher_name = "Sally"
    ))
  }
)
```


**Expected Behavior**

Process all new submissions according to the steps outlined above. 

> NOTE: actual confirmation emails are send! And the processed emails as indicated as 'read' in the Outlook environment.

**Development To Do's**

1. Showcase as part of an automated workflow

# Manual Submissions

**Goal**

Manually add a new submission to the `submission_overview`. Is useful for cases where students' submit the retakes directly to the teacher or when an assignment consists of multiple parts (e.g., Literatuurstudie).

The available information (e.g., `student_name`) are copied from earlier submission records - which should already exist in the `submission_overview`.

**Requirements**

* This code only works for students that are already included in the submission overview. For completely new students it is best to directly add the information to the Excel.

**Execution**

```{r, eval = FALSE}
add_manual_submission(student_id = 852416207,
                      submission_overview = here::here("NakijkOverzicht.xlsx"),
                      submission_date = "25/07/2022",
                      n_workdays = 20,
                      assignment = "T1")
```

**Expected Behavior**

Add a new line to the `submission_overview`.

**Development To Do's**

* Account for non-existing student information. Perhaps with a command prompt for additional information.

# Draft Grade Email

**Goal**

1. Zip all contents of the students' `grading_folder`
1. Create a draft-email with:
    1. To: `student_email`
    1. CC: examinator of the course - responsible for processing the grade.
    1. Grade-appropriate-content
    1. grading_form & relevant files (in `zip`) as attachment.

*NOTE: to change the contents of the email see the code*

**Requirements**

* This code only works for students that are included in the grading overview for a single course.

**Execution**

```{r, eval = FALSE}
draft_grade_email(
  outlook,
  submission_overview = here::here("NakijkOverzicht.xlsx"),
  grading_folder = here::here("Ingeleverde Opdrachten"),
  teacher_name = "Sally",
  student_id = 85199573)
```

**Expected Behavior**

1. Zip all contents of the students' `grading_folder`
1. Create a draft-email with:
    1. To: `student_email`
    1. CC: examinator of the course - responsible for processing the grade.
    1. Grade-appropriate-content
    1. grading_form & relevant files (in `zip`) as attachment.

**Development To Do's**

* Account for students who have taken multiple courses.
* Clean code
