---
title: "Authentication"
author: "Sally A.M. Hogenboom"
date: "`r Sys.Date()`"
format: pdf
editor_options: 
  chunk_output_type: console
---
**Setup**

```{r setup, message=FALSE}
library(yOUrEmail)
library(tidyverse)
library(magrittr)

# Authenticate & get Outlook Environment
outlook <- Microsoft365R::get_business_outlook()
```

**Goal**

Create a successful connection to the outlook environment. 
This connection allows us to read/write/send emails from an (automated) R script.

**Requirements**

  * Login credentials for our business outlook
  * An active browser (e.g., Microsoft Edge)
  * A Windows Computer
  * `install.packages("httpuv")` 
  
**Execution**

```{r authentication}
# Authenticate & get Outlook Environment
outlook <- Microsoft365R::get_business_outlook()
```

**Expected Behavior**

Upon first login this code prompts a manual login process via the browser. Working with Windows/Microsoft Edge allows for our login credentials to be saved (automatically). Therefore, upon subsequent authentication the credentials will be updated (see message output in code above).

**Development To Do's**

1. It is highly plausible that this workflow only works with a `Windows` x `Microsoft Edge` combination. Workarounds for unattended scripts (i.e., no manual steps) are available via a [Microsoft365R vignette](https://cran.r-project.org/web/packages/Microsoft365R/vignettes/scripted.html).
1. I have not been able to implement a test for an unsuccessful authentication process (see `test-authentication.R`).
1. Workflow also works for `Mac` x `DuckDuckGo` combination.

