---
title: "Drafting Feedback Emails"
author: "Sally A.M. Hogenboom"
date: "`r Sys.Date()`"
format: pdf
editor_options: 
  chunk_output_type: console
---

**Setup**

```{r setup, message=FALSE}
library(yOUrEmail)
library(tidyverse)
library(magrittr)

# Authenticate & get Outlook Environment
outlook <- Microsoft365R::get_business_outlook()
```

**Goal**

Draft a standardized email which details how to deal with feedback, where to submit the final assignment, and includes the feedback document as attachment.

**Requirements**

* Access to the files

**Execution**

```{r, eval = FALSE}
yOUrEmail::draft_feedback_email(
  outlook,
  submission_overview = here::here("NakijkOverzicht.xlsx"),
  grading_folder = here::here("Ingeleverde Opdrachten"),
  teacher_name = "Sally",
  student_id = 852258921
)
```

**Expected Behavior**

1. Create a draft-email with:
    1. To: `student_email`
    1. General 'how to process the feedback' statement
    1. Feedback document as attachment.

**Development To Do's**

* *None*
