---
title: "Drafting Grade Emails"
author: "Sally A.M. Hogenboom"
date: "`r Sys.Date()`"
format: pdf
editor_options: 
  chunk_output_type: console
---

**Setup**

```{r setup, message=FALSE}
library(yOUrEmail)
library(tidyverse)
library(magrittr)

# Authenticate & get Outlook Environment
outlook <- Microsoft365R::get_business_outlook()
```

# OEO; LS; OCO

**Goal**

Create a grade email with 'adaptive' content for all courses with a single end grade (OEO; LS; OCO).

1. Zip all contents of the students' `grading_folder`
1. Create a draft-email with:
    1. To: `student_email`
    1. CC: examinator of the course - responsible for processing the grade.
    1. Grade-appropriate-content
    1. grading_form & relevant files (in `zip`) as attachment.

*NOTE: to change the contents of the email see the code*

**Requirements**

* This code only works for the most recent submission by a student marked as 'DONE' (`status`) with a grade.

**Execution**

```{r, eval = FALSE}
draft_grade_email(
  outlook,
  submission_overview = here::here("NakijkOverzicht.xlsx"),
  grading_folder = here::here("Ingeleverde Opdrachten"),
  teacher_name = "Sally",
  student_id = 85199573)
```

**Expected Behavior**

1. Zip all contents of the students' `grading_folder`
1. Create a draft-email with:
    1. To: `student_email`
    1. CC: examinator of the course - responsible for processing the grade.
    1. Grade-appropriate-content
    1. grading_form & relevant files (in `zip`) as attachment.

**Development To Do's**

* *None*

# OKO

**Goal**

Create a grade email with 'adaptive' content for all courses with multiple grades (OKO).

1. Zip all contents of the students' `grading_folder`
1. Create a draft-email with:
    1. To: `student_email`
    1. CC: examinator of the course - responsible for processing the grade.
    1. Grade-appropriate-content
    1. grading_form & relevant files (in `zip`) as attachment.

*NOTE: to change the contents of the email see the code*

**Requirements**

* This code only works for the most recent submission by a student.
* The grade should be pipe separated (e.g., "5.5|Voldoende|6.5")

**Execution**

```{r, eval = FALSE}
yOUrEmail::draft_grade_email_OKO(
  outlook,
  submission_overview = here::here("NakijkOverzicht.xlsx"),
  grading_folder = here::here("Ingeleverde Opdrachten"),
  teacher_name = "Sally",
  student_id = 852464750
)
```

**Expected Behavior**

1. Zip all contents of the students' `grading_folder`
1. Create a draft-email with:
    1. To: `student_email`
    1. CC: examinator of the course - responsible for processing the grade.
    1. Grade-appropriate-content
    1. grading_form & relevant files (in `zip`) as attachment.

**Development To Do's**

* *None*
