---
title: "Manual Submissions (Retakes)"
author: "Sally A.M. Hogenboom"
date: "`r Sys.Date()`"
format: pdf
editor_options: 
  chunk_output_type: console
---

**Setup**

```{r setup, message=FALSE}
library(yOUrEmail)
library(tidyverse)
library(magrittr)

# Authenticate & get Outlook Environment
outlook <- Microsoft365R::get_business_outlook()
```

**Goal**

Manually add a new submission to the `submission_overview`. Is useful for cases where students' submit the retakes directly to the teacher or when an assignment consists of multiple parts (e.g., Literatuurstudie).

The available information (e.g., `student_name`) are copied from earlier submission records - which should already exist in the `submission_overview`.

**Requirements**

* This code only works for students that are already included in the submission overview. For completely new students it is best to directly add the information to the Excel.

**Execution**

```{r, eval = FALSE}
add_manual_submission(student_id = 852416207,
                      submission_overview = here::here("NakijkOverzicht.xlsx"),
                      submission_date = "25/07/2022",
                      n_workdays = 15,
                      assignment = "T1")
```

**Expected Behavior**

Add a new line to the `submission_overview`.

**Development To Do's**

* Account for non-existing student information. Perhaps with a command prompt for additional information.
