---
title: "Workflow for Automated Handling of Multiple Submission Emails"
author: "Sally A.M. Hogenboom"
date: "`r Sys.Date()`"
format: pdf
editor_options: 
  chunk_output_type: console
---

**Setup**

```{r setup, message=FALSE}
library(yOUrEmail)
library(tidyverse)
library(magrittr)

# Authenticate & get Outlook Environment
outlook <- Microsoft365R::get_business_outlook()
```

# Retrieve All Submissions

**Goal**

Retrieve all new (i.e., unread) emails from the submission system.

**Requirements**
  
**Execution**

* `outlook`: pass down the outlook environment retrieved during successful authentication
* `submissions_folder`: specify the folder where the submissions are received. 
Some teachers have automated rules set-up which move the submissions to a different *outlook*
folder (e.g., 'Nakijken'). If this is the case, specify the exact name of that folder.
* `submissions_email`: built-in option to allow for upcoming changes to the submissions system which will send the submissions from a different emailadres. Defaults to `submit@oupsy.nl`
* `email_status`: unread/read/all; only parse emails which meet the specified `status`.

```{r get-submissions}
submissions <- get_submissions(outlook,
  submissions_folder = "Nakijken",
  submissions_email = "submit@oupsy.nl",
  email_status = "unread"
)
```

**Expected Behavior**

* Retrieve a list of emails with class `ms_outlook_email`

**Development To Do's**

* *None*

# Multi Email Workflow

**Goal**

Process all the new submissions as part of an `apply` loop. For explanations of the individual processing steps see the vignette `single-email`.

**Requirements**

  * Authorization (see above)
  * All submissions (see above)
  
**Execution**

```{r, eval = FALSE}

lapply(
  X = submissions,
  FUN = function(email) {
    # Get information from the submission email
    submission_info <-
      get_submission_info(
        email = email,
        n_workdays = 20
      )

    # Create File Structure
    student_folder <-
      create_folder_structure(submission_info,
        grading_folder = "Ingeleverde Opdrachten"
      )

    # Download Attachments
    download_attachments(
      email,
      student_folder
    )

    # Add grading forms
    move_grading_form(student_folder,
      submission_info,
      grading_form_folder = "Beoordelingsformulieren"
    )

    # Update submission overview
    update_submission_overview(submission_info,
      submission_overview = here::here("NakijkOverzicht.xlsx")
    )

    # Mark email as processed
    invisible(email$update("isRead" = TRUE))

    # Send Confirmation email
    invisible(send_confirmation_email(outlook,
      submission_info,
      email,
      teacher_name = "Sally"
    ))
  }
)
```

**Expected Behavior**

Process all new submissions according to the steps outlined in the `single-email` vignette. 

**Development To Do's**

1. Showcase as part of an automated workflow (e.g., execution once a day).
